---
title: "behavior_data_BIDSdictionary"
author: "Jen Yang"
date: "created on 2024-05-16, last modified on 2025-1-27"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    hightlight: zenburn
    toc_depth: 6
---

```{r clean, include=FALSE}
# clean environment
rm(list = ls())
```

```{r restart R session, include=FALSE, results='hide'}
# .rs.restartR()
```

# Load libraries
```{r libraries, message=FALSE, warning=TRUE, include=FALSE}
library(car)
library(plyr)
library(foreign)
library(pscl)
library(boot)
library(MASS)
library(robust)
library(sfsmisc)
library(ggplot2)
library(reshape2)
library(ppcor)
library(ggrepel)
library(Hmisc)
library(tidyverse)
library(sandwich)
library(ggpubr)
library(interactions)
library(knitr)
library(twowaytests)
library(ggfortify)
library(interactions)
library(broom)
library(patchwork)
library(robustbase)
library(lmtest)
library(modelr)
library(Rmisc)
# library(raincloudplots)
library(cowplot)
library(readr)
library(PupillometryR)
library(ggpp)
library(estimatr)
library(skedastic)
library(ggpubr)
library(lubridate)
library(readxl)
library(gridExtra)
library(scales)
library(rstudioapi)
library(fs)
library(jsonlite)
library(rjson)
library(readr)
library(readxl)
```

# knit global setup
```{r}
knitr::opts_chunk$set(cache = FALSE)
```

# load functions
```{r}
source("BIDS_behavior_df_fun2.R", local = knitr::knit_global())
source("convert_csv_to_tsv_fun.R", local = knitr::knit_global())
```

# create global dataframe to save items
```{r}
items_BIDS_keep.env <- new.env()
```

# data folder directory
```{r}
google_exp2_dir = "/Users/momocco/Library/CloudStorage/GoogleDrive-tun51150@temple.edu/.shortcut-targets-by-id/1Yd_mABZr2-erO8s2c0GuJSs36TfUycDa/Limited_Info/Experiment_2/bids"
google_exp1_dir = "/Users/momocco/Library/CloudStorage/GoogleDrive-tun51150@temple.edu/.shortcut-targets-by-id/1Yd_mABZr2-erO8s2c0GuJSs36TfUycDa/Limited_Info/Experiment_1/risk_amb/data"

git_OSF_exp2_dir = "/Users/Momocco/Documents/GitHub/risk-ambiguity/dissenminate/OSF_upload/beh_risk_amb_Exp2"
git_OSF_exp1_dir = "/Users/Momocco/Documents/GitHub/risk-ambiguity/dissenminate/OSF_upload/beh_risk_amb_Exp1"
```

# Exp 2
## load participant list
```{r}
participants_exp2_df = read_tsv(paste(git_OSF_exp2_dir, "participants.tsv", sep = "/"), show_col_types = FALSE)
participants_exp2_list = participants_exp2_df$participant_id
```

## copy, modify, rename
```{r}
## rename files (change _events.tsv to _beh.tsv)
old_substring <- "_events.tsv"
new_substring <- "_beh.tsv"
old_mem_substring <- "_mem-report.tsv"
new_mem_substring <- "_task-memory_beh.tsv"

for (f in 1:length(participants_exp2_list)) {
  # f = 1
  ## copy entire subject folder from jeff's folder to OSF_upload folder
  ### Specify the source and destination paths
  source_folder <- paste(google_exp2_dir, participants_exp2_list[f], sep = "/")
  destination_folder <- git_OSF_exp2_dir
  
  ### Copy the entire folder structure
  file.copy(from = source_folder, 
            to = destination_folder, 
            recursive = TRUE, 
            overwrite = TRUE)
  
  ### rename copied files
  OSF_sub_path = paste(git_OSF_exp2_dir, participants_exp2_list[f], sep = "/")
  old_files <- list.files(path = OSF_sub_path)
  
  # Create new names by replacing the substring
  new_names <- str_replace_all(old_files, old_substring, new_substring)
  new_names <- str_replace_all(new_names, old_mem_substring, new_mem_substring)
  
  # Rename the files
  file.rename(from = file.path(OSF_sub_path, old_files), to = file.path(OSF_sub_path, new_names))
}
```

## modify column name
```{r}
## Define the old and new column names
risk_old_colname <- "p1"
amb_old_colname = "per"
learn_old_colname = "per"
new_colname <- "winprob"

for (f in 1:length(participants_exp2_list)) {
  # f = 1
  # print(f)
  OSF_sub_path = paste(git_OSF_exp2_dir, participants_exp2_list[f], sep = "/")
  tsv_files <- list.files(path = OSF_sub_path, pattern = "\\.tsv$", full.names = TRUE)
 
  for (i in 1:length(tsv_files)) {
    # i = 2
    # print(i)
    if (endsWith(tsv_files[i], "task-amb_run-1_beh.tsv") == TRUE ) {
      task_current_df = read.table(file = tsv_files[i], sep = '\t', header = TRUE)
      if (amb_old_colname %in% colnames(task_current_df)) {
      task_current_df = task_current_df %>% 
        rename(!!new_colname := !!sym(amb_old_colname))
      write_tsv(task_current_df, tsv_files[i])
      }
    } else if (endsWith(tsv_files[i], "task-risk_run-1_beh.tsv") == TRUE ) {
      task_current_df = read.table(file = tsv_files[i], sep = '\t', header = TRUE)
      if (risk_old_colname %in% colnames(task_current_df)) {
      task_current_df = task_current_df %>% 
        rename(!!new_colname := !!sym(risk_old_colname))
      write_tsv(task_current_df, tsv_files[i])
      }
    } else if (endsWith(tsv_files[i], "task-learn_run-1_beh.tsv") == TRUE ) {
      task_current_df = read.table(file = tsv_files[i], sep = '\t', header = TRUE)
      if (learn_old_colname %in% colnames(task_current_df)) {
      task_current_df = task_current_df %>% 
        rename(!!new_colname := !!sym(learn_old_colname))
      write_tsv(task_current_df, tsv_files[i])
      }
    }
  }
}
```

## behavior json
### load meta info
```{r}
# directory
meta_dir = "/Users/Momocco/Documents/GitHub/risk-ambiguity-DataInBrief/data_dictionary"

# from the main spreadsheet
main_behavior_spreadsheet = read_excel(paste(meta_dir, "BehaviorMeta_Exp2.xlsx", sep = "/"))

# directly from session project RedCap
behavior_dictionary = read_excel(paste(meta_dir, "BehaviorDict_Exp2.xlsx", sep = "/"))

# from the scoring spreadsheet
task_dictionary = read_excel(paste(meta_dir,"BehaviorTaskMap_Exp2.xlsx", sep = "/"))
```

### memory report
```{r}
task_name = "memory"
for (f in 1:length(participants_exp2_list)) {
  # f = 2
  if (startsWith(participants_exp2_list[f], "sub-") == TRUE ) {
    OSF_sub_path_partial = paste(git_OSF_exp2_dir, participants_exp2_list[f], participants_exp2_list[f], sep = "/")
    BIDS_pheno = BIDS_behavior_df_fun2(task_name, main_behavior_spreadsheet,
                                    behavior_dictionary, 
                                    task_dictionary, OSF_sub_path_partial)
  }
}
```

### risk task
```{r}
task_name = "risk"
for (f in 1:length(participants_exp2_list)) {
  # print(f)
  if (startsWith(participants_exp2_list[f], "sub-") == TRUE ) {
    OSF_sub_path_partial = paste(git_OSF_exp2_dir, participants_exp2_list[f], participants_exp2_list[f], sep = "/")
    BIDS_pheno = BIDS_behavior_df_fun2(task_name, main_behavior_spreadsheet,
                                       behavior_dictionary, 
                                       task_dictionary, OSF_sub_path_partial)
  }
}
```

### ambiguity task
```{r}
task_name = "amb"
for (f in 1:length(participants_exp2_list)) {
  # f = 2
  if (startsWith(participants_exp2_list[f], "sub-") == TRUE ) {
    OSF_sub_path_partial = paste(git_OSF_exp2_dir, participants_exp2_list[f], participants_exp2_list[f], sep = "/")
    BIDS_pheno = BIDS_behavior_df_fun2(task_name, main_behavior_spreadsheet,
                                       behavior_dictionary, 
                                       task_dictionary, OSF_sub_path_partial)
  }
}
```

### learning task
```{r}
task_name = "learn"
for (f in 1:length(participants_exp2_list)) {
  # f = 2
  if (startsWith(participants_exp2_list[f], "sub-") == TRUE ) {
    OSF_sub_path_partial = paste(git_OSF_exp2_dir, participants_exp2_list[f], participants_exp2_list[f], sep = "/")
    BIDS_pheno = BIDS_behavior_df_fun2(task_name, main_behavior_spreadsheet,
                                       behavior_dictionary, 
                                       task_dictionary, OSF_sub_path_partial)
  }
}
```

## create beh folder for each sub
```{r}
beh_folder = "beh"

for (f in 1:length(participants_exp2_list)) {
  # f = 2
  if (startsWith(participants_exp2_list[f], "sub-") == TRUE) {
    sub_f_path <- paste(git_OSF_exp2_dir, participants_exp2_list[f],sep = "/")
    beh_folder_path <- file.path(sub_f_path, beh_folder)
    dir_create(beh_folder_path)
    # List all files in current sub folder
    all_files <- dir_ls(sub_f_path, type = "file")
    if (length(all_files)==0) {
      print(paste("no files in ", sub_f_path, sep = ""))
    } else {
      # Move all files to the new subfolder
      for (file in all_files) {
        file_move(file, beh_folder_path)
      }
    }
  }
}
```

# Exp 1
## load participant list
```{r}
participants_exp1_df = read_tsv(paste(git_OSF_exp1_dir, "participants.tsv", sep = "/"), show_col_types = FALSE)
participants_exp1_list = participants_exp1_df$participant_id
```

## convert file type, rename
```{r}
old_substring <- "_events.tsv"
new_substring <- "_beh.tsv"
for (f in 1:length(participants_exp1_list)) {
  # f = 1
  if (startsWith(participants_exp1_list[f], "sub-") == TRUE ) {
    # copy from google folder
    google_OSF_sub_path = paste(google_exp1_dir, participants_exp1_list[f], sep = "/")
    OSF_sub_path = paste(git_OSF_exp1_dir, participants_exp1_list[f], sep = "/")
    
    ## create sub folder if doesn't exist
    if (!dir.exists(OSF_sub_path)) {
      dir.create(OSF_sub_path)
    }
    
    csv_files <- list.files(path = google_OSF_sub_path, 
                       pattern = "\\.csv$", 
                       full.names = TRUE)
    file.copy(from = csv_files, 
         to = OSF_sub_path, 
         overwrite = FALSE)

    OSF_sub_path = paste(git_OSF_exp1_dir, participants_exp1_list[f], sep = "/")
    
    # list all .csv files
    csv_files <- list.files(path = OSF_sub_path, pattern = "\\.csv$", full.names = TRUE)
    # convert all .csv to .tsv
    lapply(csv_files, convert_csv_to_tsv_fun)
    # Create new names by replacing the substrings
    old_files = list.files(path = OSF_sub_path, pattern = "\\.tsv$")
    new_names <- str_replace_all(old_files, old_substring, new_substring)
    
    # Rename the files
    file.rename(from = file.path(OSF_sub_path, old_files), to = file.path(OSF_sub_path, new_names))
  }
}
```

## behavior json
### load meta info
```{r}
# directory
meta_dir = "/Users/Momocco/Documents/GitHub/risk-ambiguity-DataInBrief/data_dictionary"

# from the main spreadsheet
main_behavior_spreadsheet = read_excel(paste(meta_dir, "BehaviorMeta_Exp1.xlsx", sep = "/"))

# directly from session project RedCap
behavior_dictionary = read_excel(paste(meta_dir, "BehaviorDict_Exp1.xlsx", sep = "/"))

# from the scoring spreadsheet
task_dictionary = read_excel(paste(meta_dir,"BehaviorTaskMap_Exp1.xlsx", sep = "/"))
```

### risk task
```{r}
task_name = "risk"
for (f in 1:length(participants_exp1_list)) {
  # f = 2
  file_name = paste(participants_exp1_list[f], "task-risk", "beh.tsv", sep = "_")
  file_path = paste(git_OSF_exp1_dir, participants_exp1_list[f], file_name, sep = "/")
  if (file.exists(file_path)) {
    OSF_sub_path_partial = paste(git_OSF_exp1_dir, participants_exp1_list[f], participants_exp1_list[f], sep = "/")
    BIDS_pheno = BIDS_behavior_df_fun2(task_name, main_behavior_spreadsheet,
                                       behavior_dictionary, 
                                       task_dictionary, OSF_sub_path_partial)
  } else {
    print(paste(file_name, "doesn't exist.", sep = " "))
  }
}
```

### ambiguity task
```{r}
task_name = "ambiguity"
for (f in 1:length(participants_exp1_list)) {
  # f = 2
  file_name = paste(participants_exp1_list[f], "task-ambiguity", "beh.tsv", sep = "_")
  file_path = paste(git_OSF_exp1_dir, participants_exp1_list[f], file_name, sep = "/")
  if (file.exists(file_path)) {
    OSF_sub_path_partial = paste(git_OSF_exp1_dir, participants_exp1_list[f], participants_exp1_list[f], sep = "/")
    BIDS_pheno = BIDS_behavior_df_fun2(task_name, main_behavior_spreadsheet,
                                       behavior_dictionary, 
                                       task_dictionary, OSF_sub_path_partial)
  } else {
    print(paste(file_name, "doesn't exist.", sep = " "))
  }
}
```

## create beh folder for each sub following BIDS
```{r}
beh_folder = "beh"

for (f in 1:length(participants_exp1_list)) {
  # f = 2
  if (startsWith(participants_exp1_list[f], "sub-") == TRUE) {
    sub_f_path <- paste(git_OSF_exp1_dir, participants_exp1_list[f],sep = "/")
    beh_folder_path <- file.path(sub_f_path, beh_folder)
    dir_create(beh_folder_path)
    # List all files in current sub folder
    all_files <- dir_ls(sub_f_path, type = "file")
    if (length(all_files)==0) {
      print(paste("no files in ", sub_f_path, sep = ""))
    } else {
      # Move all files to the new subfolder
      for (file in all_files) {
        file_move(file, beh_folder_path)
      }
    }
  }
}
```

